% ============================================================================
% SECTION 5.2: Challenges, Solutions, and Professional Growth (Rubric: Discussion - Weight 2)
% ============================================================================
% TODO: Add your content here
% This file maps to the rubric-optimized report structure
% ============================================================================

% Add your LaTeX content below this line

Our biggest challenge was not being able to secure weekly stakeholder feedback, although our project manager did give us a wealth of suggestions each week.
We began with paper sketches to map out data flow and identify key system components. We decided the map system would include a cartoon mode, a 3D view, and a GIS layer all linked to our story module and database.
Next, we researched existing platforms layers of London and Green stone digital library that combine mapping with storytelling to inform our approach.
With those examples in mind, we moved on to designing our wireframes, starting with the homepage. We sketched out a sidebar featuring Home, Layer, Search, and Explore, then stretched those ideas into a more detailed layout.
We sketched out a sidebar featuring Home, Layer, Search, and Explore, then stretched those ideas into a more detailed layout. After that, we added a footer and cartoon-mode verification functionality to our design.
We decided to use HTML and JavaScript to build our website and Bootstrap for our user tour and presentation, since we believed this would be an efficient way to onboard first-time visitors. During this process, we learned how to use Figma, manage a project, and collaborate with people from different cultures. Eventually, we were able to provide weekly updates to our project manager.


